---
title: "Comparison of Cylinder Count to Engine Displacement"
author: "Varya Kern"
date: "2025-07-31"
output: html_document
---

This report, commissioned by the illustrious and eminent Big Dawg, will investigate whether cars with more cylinders have more engines, or whether this is a lie fabricated by undercover communists and blue-haired liberal butterflies. The default R dataset 'mtcars' will be used and both tabular and graphical methods used to compare engine displacement for each cylinder count (4, 6, or 8).

```{r mtcars_table}
 dt <- mtcars |> select(cyl, disp)
 dt_summary <- dt %>% group_by(cyl) %>% 
   summarize(disp_m = round(mean(disp), 2)) %>% 
   rename("Cylinders" = cyl, "Displacement" = disp_m)
  
knitr::kable(dt_summary, caption = "Table 1: Mean engine displacement by number of cylinders.") %>%
  kableExtra::kable_classic(full_width = F, position = "center", html_font = "Computer Modern Roman")
```
```{r mtcars_chart}
dt_summary %>% ggplot(aes(x=Cylinders, y=Displacement)) + geom_col() + theme_classic() + labs(x="Number of Cylinders", y="Engine Displacement (cm^3)", title = "Figure 1. Mean engine displacement by number of cylinders.")
```
